Quality Definitions of Qualities

### 2020-01-19 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
update consistency

\begin{defn}
  The use of uniform design and implementation techniques and notations
  throughout a project \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Ao, if this is from McCall, we should just cite
    the primary source and remove the Van Vliet reference.} \pmi{McCall's definition verbatim: Those attributes of the software that provide uniform design and implementation techniques and notation.}
\end{defn}

>>>>

\begin{defn}
  Those attributes of the software that provide uniform design and 
  implementation techniques and notation \citep{McCallEtAl1977}.  \wss{Ao, if 
  this is from McCall, we should just cite
    the primary source and remove the Van Vliet reference.} \pmi{McCall's 
    definition verbatim: Those attributes of the software that provide uniform 
    design and implementation techniques and notation.}\ad{Originally added 
  by someone else so I didn't have access to the book. But now it's available 
  and I double checked, Peter got it accurately.}
\end{defn}
